Conflict Driven Evolution and Urban Development: \\ Evidence from the Holy Roman Empire\footnote{ I thank Lara Andermann, Leonie Bielefeld, Daniel Bursian, Davide Cantoni, Emilio Esguerra, Filip Milojevic, Johannes Vorbach and Matthias Weigand for helpful comments and feedback. }

### 2023-06-26 paper/output/regressions/robustness_50y.tex
#29 cut caption of table 4
#29 fix typo in header

\begin{table}[htbp]
   \caption{\label{tab:robustness_50y} Heterogeneous effects of switching: More robustness}
   \centering
   \begin{tabular}{lcccc}
      \tabularnewline \midrule \midrule
      Dependent Variable: & \multicolumn{4}{c}{All construction}\\
                                                 & Baseline & 4 Switches   & All switches & Window \\   
      Model:                                     & (1)      & (2)          & (3)          & (4)\\  
      \midrule
      \emph{Variables}\\
      Switch to another state                    & 0.02     & 0.04$^{***}$ & 0.02$^{***}$ & 0.02\\   
                                                 & (0.03)   & (0.01)       & (0.01)       & (0.02)\\   
      Switch to another state $\times$ Conquest  & 0.04     & 0.03         & -0.01        & 0.04\\   
                                                 & (0.04)   & (0.02)       & (0.01)       & (0.04)\\   
      Switch to another state $\times$ Other     & 0.01     & -0.02        & 0.00         & 0.01\\   
                                                 & (0.03)   & (0.01)       & (0.01)       & (0.03)\\   
      Switching indicator                        & -0.01    & -0.02        & -0.01        & -0.01\\   
                                                 & (0.02)   & (0.02)       & (0.01)       & (0.02)\\   
      \midrule
      \emph{Fixed-effects}\\
      City                                       & Yes      & Yes          & Yes          & Yes\\  
      Period                                     & Yes      & Yes          & Yes          & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                               & 6,635    & 12,979       & 31,754       & 6,635\\  
      R$^2$                                      & 0.3553   & 0.3664       & 0.3518       & 0.3553\\  
      Within R$^2$                               & 0.0009   & 0.0019       & 0.0003       & 0.0009\\  
      \midrule \midrule

@@

   \par \raggedright 
   Note: Table presents results of estimation equation \eqref{eq:baseline}. Column (1) uses the baseline sample, Column (2) includes cities with up to 4 lifetime switches, Column (3) includes all cities regardless of the number of lifetime switches, and Column (4) uses a post-treatment indicator that is only active in the first 200 years after the treatment. Dependent variable is "All construction" in  all regressions.The switch type "Succession" is omitted as the reference category. Yearly data was aggregated into periods of 50 years. Observations are at the city-period level. Standard errors are  clustered at the city level. *, **, and *** denote significance on the 10 percent, 5 percent, and 1 percent  level, respectively.
\end{table}

>>>>

\begin{table}[htbp]
   \caption{\label{tab:robustness_50y} Heterogeneous effects of switching: More robustness}
   \centering
   \begin{tabular}{lcccc}
      \tabularnewline \midrule \midrule
      Dependent Variable: & \multicolumn{4}{c}{All construction}\\
                                                 & Baseline & 4 switches   & All switches & Window \\   
      Model:                                     & (1)      & (2)          & (3)          & (4)\\  
      \midrule
      \emph{Variables}\\
      Switch to another state                    & 0.02     & 0.04$^{***}$ & 0.02$^{***}$ & 0.02\\   
                                                 & (0.03)   & (0.01)       & (0.01)       & (0.02)\\   
      Switch to another state $\times$ Conquest  & 0.04     & 0.03         & -0.01        & 0.04\\   
                                                 & (0.04)   & (0.02)       & (0.01)       & (0.04)\\   
      Switch to another state $\times$ Other     & 0.01     & -0.02        & 0.00         & 0.01\\   
                                                 & (0.03)   & (0.01)       & (0.01)       & (0.03)\\   
      Switching indicator                        & -0.01    & -0.02        & -0.01        & -0.01\\   
                                                 & (0.02)   & (0.02)       & (0.01)       & (0.02)\\   
      \midrule
      \emph{Fixed-effects}\\
      City                                       & Yes      & Yes          & Yes          & Yes\\  
      Period                                     & Yes      & Yes          & Yes          & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                               & 6,635    & 12,979       & 31,754       & 6,635\\  
      R$^2$                                      & 0.3553   & 0.3664       & 0.3518       & 0.3553\\  
      Within R$^2$                               & 0.0009   & 0.0019       & 0.0003       & 0.0009\\  
      \midrule \midrule

@@

   \par \raggedright 
   Note: Table presents results of estimation equation \eqref{eq:baseline}. Column (1) uses the baseline sample, Column (2) includes cities with up to 4 lifetime switches, Column (3) includes all cities regardless of the number of lifetime switches, and Column (4) uses a post-treatment indicator that is only active in the first 200 years after the treatment. Yearly data was aggregated into periods of 50 years. Observations are at the city-period level. Standard errors are  clustered at the city level. *, **, and *** denote significance on the 10 percent, 5 percent, and 1 percent  level, respectively.
\end{table}
